IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-05-11 paper/appendix.tex
Update erasure function for extentions.

\begin{figure}
  %{
  %format .->  = "\overset{\alpha}{\hookrightarrow}"
  %format .-/>  = "\not\overset{\alpha}{\hookrightarrow}"
  \begin{code}
    iv  ::= cdots | ial
    ie  ::= cdots | new ie ie | read ie | write ie ie
    iE  ::= cdots | new iE ie | new il iE | read E
                  | write iE ie | write ial iE
  \end{code}

@@

\begin{figure}
  \begin{align*}
  &|erase il (iconf iS its) =
  iconf (erase il iS) (fltr (\ it . it = bullet) (map (erasef il) its))|\\
  &|fullconf id il' tS ie| \begin{cases}
  |bullet| & |il' cantFlowTo il| \\
  |fullconf id il' (erase il tS) (erase il ie)| & \text{otherwise}
  \end{cases} \\
  &|erase il emptyset = emptyset|\\
  &|erase il (bracket iS (mapsto id Q)) =| \begin{cases}
  |erase il iS| & \text{|il' cantFlowTo il|, where |il'| is}\\
  & \text{the label of thread |id|} \\
  |bracket (erase il iS) (mapsto id (erase il Q))| & \text{otherwise}
  \end{cases} \\
  &|erase il Q = filter il Q|\\
  &|erase il v = v|
  \end{align*}
  \caption{Erasure function for the full IFC language, with all extensions.
    In all not specified (including target-language constructs),
    |erasef il| is applied homomorphically.}
  \label{fig:erasure2}
\end{figure}

>>>>

\begin{figure}
  %{
  %format .->  = "\overset{\alpha}{\hookrightarrow}"
  %format .-/>  = "\not\overset{\alpha}{\hookrightarrow}"
  \begin{code}
    iv  ::= cdots | ial
    ie  ::= cdots | new ie ie | read ie | write ie ie
    iE  ::= cdots | new iE ie | new il iE | read E
                  | write iE ie | write ial iE
    iS  ::=  cdots | bracket iS (mapsto ial iv)
  \end{code}

@@

\begin{figure}
  \begin{align*}
  &|erase il (iconf iS its) =
  iconf (erase il iS) (fltr (\ it . it = bullet) (map (erasef il) its))|\\
  &|fullconf id il' tS ie| \begin{cases}
  |bullet| & |il' cantFlowTo il| \\
  |fullconf id il' (erase il tS) (erase il ie)| & \text{otherwise}
  \end{cases} \\
  &|erase il (Labeled il' ie)|= \begin{cases}
  |Labeled il' bullet| & |il' cantFlowTo il| \\
  |Labeled il' ie| & \text{otherwise}
  \end{cases} \\
  &|erase il emptyset = emptyset|\\
  &|erase il (bracket iS (mapsto id Q)) =| \begin{cases}
  |erase il iS| & \text{|il' cantFlowTo il|, where |il'| is}\\
  & \text{the label of thread |id|} \\
  |bracket (erase il iS) (mapsto id (erase il Q))| & \text{otherwise}
  \end{cases} \\
  &|erase il (bracket iS (mapsto (iall il') iv)) =| \begin{cases}
  |bracket (erase il iS) (mapsto (iall il') bullet)| & \text{|il' cantFlowTo il|}\\
  |bracket (erase il iS) (mapsto (iall il') (erase il iv))| & \text{otherwise}
  \end{cases} \\
  &|erase il Q = filter il Q|
  \end{align*}
  \caption{Erasure function for the full IFC language, with all extensions.
    In all cases not specified (including target-language constructs),
    |erasef il| is applied homomorphically.
    This definition replaces the one from Figure~\ref{fig:erasure}, which
    is for the IFC language without extensions.}
  \label{fig:erasure2}
\end{figure}
